---
title: "Progress Report 3"
subtitle: "Activity: A Gentle Introduction to Bayesian Statistics"
format: html
author: 
  - name: Laurie Baker (Bates College)
  - name: Jim Scott (Colby College)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(plan)
library(dplyr)
```

## Overview

In the final part of the project we finalized drafts for several lab assignments. In our November meeting with Mine, we discussed our drafts for several lab assignments and incorporated feedback.

- **CNN vs. The Onion:** is an activity from Jim's class where students decide on whether a headline was generated by CNN or the Onion. We developed a lab where students could gain familiarity with the Binomial distribution and where the data could be used to introduce the Beta-Binomial model and show how our choice of priors influence the posteriors. 

- **Ecuador Village Social Connectivity:** is another activity from Jim's class where students look at real data derived from a study of diarrheal disease transmission in Ecuador. We decided to use this example to develop a lab to familiarize students with simple linear regression.
- **Webr tutorials introducing R and probability concepts:** We developed several web-r tutorials that build on exercises that accompany readings from Stat20.org. The webr format allows students to practice R code without having to download and install RStudio. We developed tutorials to accompany the units on introduction to probability, random variables, and normal and continuous distributions.   

## Completed Materials

We have created drafts of the following:

- [CNN vs Onion](https://bayes-bats.github.io/tier2-short-term/course-materials/labs/beta_binomial_cnn_vs_onion/cnn_vs_onion.html) - Introducing `dbinom`, `pbinom`, and `rbinom` the Binomial distribution

- [TB Outbreak at the Zoo](https://bayes-bats.github.io/tier2-short-term/course-materials/labs/zoo-outbreak/ZooOutbreak.html) - We have drafted the background for this dataset and could build on this assignment at a later date. However, we felt that it would be better to structure this .
- [CNN vs Onion Beta-Binomial](https://bayes-bats.github.io/tier2-short-term/course-materials/labs/beta_binomial_cnn_vs_onion/cnn_vs_onion_beta_binomial.html) - this lab covers priors and introduces the Beta-Binomial including plotting prior and posterior distributions and calculating summary statistics for this distribution.

- **Probability WebR Labs**

We also have created a number of Probability labs to accompany the readings from [Stat20](stat20.org) which is a creative commons resource that we plan to use when covering some of the probability concepts in our course. Currently these exercises are at the end of the readings but are not able to be practiced actively without copying and pasting the code.

We plan to share these webr tutorials with Andrew Bray and colleagues at UC Berkeley who authored the course. The webr tutorials we have finished include:

- [Introduction to R and Sampling Functions](../course-materials/labs/intro_probability_webr_labs/lab-intro-r-and-sampling-functions.html)

- [Random Variables - Introducing Binomial, Poisson, and Hypergeometric Distributions](../course-materials/labs/intro_probability_webr_labs/random_variables_binomial_poisson.html)

Our future plans include creating a problem set in learnr where students will complete and be graded on these problems. Adam Gilbert from Southern New Hampshire University has shared a template with Laurie.

- **Tier 3 Proposal** Laurie and Jim have started discussing applying for Tier 3. Laurie is thinking about applying to present some of the work at UKCOTS in Glasgow, Scotland. Laurie has selected this venue because it will be a good opportunity to share ideas with UK undergraduate professors teaching statistics and there will be the opportunity to bring back curriculum ideas to the US from this conference. Laurie and Jim have also discussed ideas about upcoming epidemiological conferences which might be a good venue for this work.

## Updated Gantt Chart

```{r, echo=FALSE}
g <- new("gantt")
g <- ganttAddTask(g, "Work Plan")
g <- ganttAddTask(g, "Syllabus Development","2024-09-03","2024-10-03", done=85)
g <- ganttAddTask(g, "Draft Homework and Activity Plan", "2024-09-20","2024-10-03", done=100)
g <- ganttAddTask(g, "Progress Report 1")
g <- ganttAddTask(g, "Develop Draft of Activities 1-2", "2024-10-04", "2024-10-17", done=60)
g <- ganttAddTask(g, "Develop Draft of Activities 3-4", "2024-10-17", "2024-11-04", done=75)
g <- ganttAddTask(g, "Submit Tier 3 Proposal", "2024-10-17", "2024-10-24", done=0)
g <- ganttAddTask(g, "Progress Report 2")
g <- ganttAddTask(g, "Finalize Activity 1-2", "2024-11-03", "2024-11-17", done=0)
g <- ganttAddTask(g, "Finalize Activity 3-4", "2024-11-17", "2024-12-03", done=0)
g <- ganttAddTask(g, "Final Materials Submission")
g <- ganttAddTask(g, "Finalize applied R activity", "2024-12-01", "2024-12-10", done=0)
g <- ganttAddTask(g, "Finalize all activities and syllabus", "2024-12-10", "2024-12-14", done=0)


font <- ifelse(is.na(g[["start"]]), 2, 1)

plan::plot(g, ylabels=list(font=font),
     event.label='Progress Report 2', event.time='2024-11-01',
     col.event=c("firebrick2"),
     col.done=c("steelblue3"),
     col.notdone=c("palegreen3"),
     cex.main=1,
     main="Tier 2: Gentle Intro to Probability and Bayesian Statistics",
     )

legend("topright", pch=22, pt.cex=2, cex=0.6, pt.bg=c("steelblue3", "palegreen3"),
     border="black",
     legend=c("Completed", "Incomplete"), bg="white", xpd=TRUE)

```


## Acknowledgements

This report template comes from Zachary Del Rosario and Stefani Langehennig's [Bayes-Bats tier 2 project](https://github.com/bayes-bats/tier2-freq-bayes)
