---
title: "Progress Report Template"
subtitle: "Activity: Short-term course"
format: html
author: 
  - name: Laurie Baker (Bates College)
  - name: Jim Scott (Colby College)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(plan)
library(dplyr)
```

## Overview



## Updated Gantt Chart

This is an example gantt chart

```{r, echo=FALSE}
g <- new("gantt")
g <- ganttAddTask(g, "Work Plan")
g <- ganttAddTask(g, "Syllabus Development","2024-09-03","2024-10-03", done=0)
g <- ganttAddTask(g, "Draft Homework and Activity Plan", "2024-09-20","2024-10-03", done=0)
g <- ganttAddTask(g, "Progress Report 1")
g <- ganttAddTask(g, "Develop Draft of Activities 1-2", "2024-10-04", "2024-10-17", done=0)
g <- ganttAddTask(g, "Develop Draft of Activities 3-4", "2024-10-17", "2024-11-04", done=0)
g <- ganttAddTask(g, "Submit Tier 3 Proposal", "2024-10-17", "2024-10-24", done=0)
g <- ganttAddTask(g, "Progress Report 2")
g <- ganttAddTask(g, "Finalize Activity 1-2", "2024-11-03", "2024-11-17", done=0)
g <- ganttAddTask(g, "Finalize Activity 3-4", "2024-11-17", "2024-12-03", done=0)
g <- ganttAddTask(g, "Final Materials Submission")
g <- ganttAddTask(g, "Finalize applied R activity", "2024-12-01", "2024-12-10", done=0)
g <- ganttAddTask(g, "Finalize all activities and syllabus", "2024-12-10", "2024-12-14", done=0)


font <- ifelse(is.na(g[["start"]]), 2, 1)

plot(g, ylabels=list(font=font),
     event.label='Submit Final Materials',event.time='2024-12-03',
     col.event=c("firebrick2"),
     col.done=c("steelblue3"),
     col.notdone=c("palegreen3"),
     cex.main=1,
     main="Tier 2: Gentle Intro to Probability and Bayesian Statistics",
     )

legend("topright", pch=22, pt.cex=2, cex=0.6, pt.bg=c("steelblue3", "palegreen3"),
     border="black",
     legend=c("Completed", "Incomplete"), bg="white", xpd=TRUE)

```

## Completed Materials


## Next Steps

## Meeting Times

We will keep meeting based on the following:

-   Weekly meetings for the activity-creating team
-   Monthly meetings with mentor (Mine)
-   Office hours

| Date       | Time               | PI     | Zoom Link |
|------------|--------------------|--------|-----------|
| 2024-09-06 | 3:00 - 4:00 pm ET      | Amy |         |
| 2024-09-18 | 3:30 - 4:30 pm ET | Monika |  [`r fontawesome::fa(name = "video")`](https://vassar.zoom.us/my/monika76five)        |
| 2024-09-26 | 2:00 - 3:00 pm ET  | Mine    |[`r fontawesome::fa(name = "video")`](https://uci.zoom.us/j/91799232149)          |
| 2024-10-07 | 3:30 - 4:30 pm ET | Monika |  [`r fontawesome::fa(name = "video")`](https://vassar.zoom.us/my/monika76five)        |
| 2024-10-15 | 3:00 - 4:00 pm ET      | Amy |         |
| 2024-10-2? | | Mine | |
| 2024-11-0? | | Mine | |
| 2024-11-12 | 3:00 - 4:00 pm ET      | Amy |         |
| 2023-11-20 | 3:30 - 4:30 pm ET | Monika |  [`r fontawesome::fa(name = "video")`](https://vassar.zoom.us/my/monika76five)        |


## Acknowledgements

This report template comes from Zachary Del Rosario and Stefani Langehennig's [Bayes-Bats tier 2 project](https://github.com/bayes-bats/tier2-freq-bayes)
