---
title: "Progress Report 2"
subtitle: "Activity: A Gentle Introduction to Bayesian Statistics"
format: html
author: 
  - name: Laurie Baker (Bates College)
  - name: Jim Scott (Colby College)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(plan)
library(dplyr)
```

## Overview

In the second part of the project we began creating the drafts for several lab assignments. In our October meeting with Mine, we shared a draft of plans for activities we will develop for the course.

- **CNN vs. The Onion:** is an activity from Jim's class where students decide on whether a headline was generated by CNN or the Onion. We determined that this would be a good example for gaining familiarity with the Binomial distribution and could be used to introduce the Beta-Binomial and show how our choice of prior influence the posteriors. 

- **Outbreak at the Zoo:** is another activity from Jim's class where students look at real data derived from a Tuberculosis outbreak that affected zoo staff, elephants, and other animals at the zoo. This dataset has a range of possibilities including inference on proportions. 
- **Webr and learnr tutorials introducing R and probability concepts:** We also discussed the need to give students hands-on practice with R and with probability distributions in the first part of the course. Laurie will work on developing probabilty web-r tutorials that build on exercises from readings from Stat20. The webr format allows students to practice R code without having to download and install RStudio. We felt that this was a useful first step, particularly for an introductory course. 

## Completed Materials

We have created drafts of the following:

- [CNN vs Onion](https://bayes-bats.github.io/tier2-short-term/course-materials/labs/beta_binomial_cnn_vs_onion/cnn_vs_onion.html) - Introducing `dbinom`, `pbinom`, and `rbinom` the Binomial distribution
    - Before our meeting with Mine, Laurie will explore creating a google form where students can complete the quiz and the data can be stored and then downloaded from an RShiny app where individuals can download their own classes data and also everyone who has taken the quiz's responses.

- [TB Outbreak at the Zoo](https://bayes-bats.github.io/tier2-short-term/course-materials/labs/zoo-outbreak/ZooOutbreak.html) - We have drafted the background for this dataset and will develop a set of questions and ideas for how this lab could be structured.
- [CNN vs Onion Beta-Binomial - Under Construction](https://bayes-bats.github.io/tier2-short-term/course-materials/labs/beta_binomial_cnn_vs_onion/cnn_vs_onion_beta_binomial.html) - priors and introducing the beta-Binomial. We are currently still developing this and hope to have a little more progress by our meeting with Mine in November. We plan to model this lab after the Bechdel example in these slides on [*Different Priors, Different Posteriors*](https://bayes-bats.github.io/bootcamp-materials-2024/day-1-foundations/2-lec-discrete-data/2-lec-discrete-data.html#/different-priors-different-posteriors) from the Bayes Bats Day 1 Foundations slides. We will draft a set of questions for Mine before our meeting about structuring this lab.

- **Probability WebR Labs**

We also have created a number of Probability labs to accompany the readings from [Stat20](stat20.org) which is a creative commons resource that we plan to use when covering some of the probability concepts in our course. Currently these exercises are at the end of the readings but are not able to be practiced actively without copying and pasting the code.

We plan to share these webr tutorials with Andrew Bray and colleagues at UC Berkeley who authored the course. The webr tutorials we have started developing are:

- [Introduction to R and Sampling Functions](../course-materials/labs/intro_probability_webr_labs/lab-intro-r-and-sampling-functions.html)

- [Random Variables - Introducing Binomial, Poisson, and Hypergeometric Distributions](../course-materials/labs/intro_probability_webr_labs/random_variables_binomial_poisson.html)

We plan to create a problem set in learnr where students will complete and be graded on these problems. Adam Gilbert from Southern New Hampshire University has shared a template with Laurie.

- **Tier 3 Proposal** Laurie and Jim have started discussing applying for Tier 3. Laurie is thinking about applying to present some of the work at UKCOTS in Glasgow, Scotland. Laurie has selected this venue because it will be a good opportunity to share ideas with UK undergraduate professors teaching statistics and there will be the opportunity to bring back curriculum ideas to the US from this conference. Laurie and Jim have also discussed ideas about upcoming epidemiological conferences which might be a good venue for this work.

## Updated Gantt Chart

This is an example gantt chart

```{r, echo=FALSE}
g <- new("gantt")
g <- ganttAddTask(g, "Work Plan")
g <- ganttAddTask(g, "Syllabus Development","2024-09-03","2024-10-03", done=85)
g <- ganttAddTask(g, "Draft Homework and Activity Plan", "2024-09-20","2024-10-03", done=100)
g <- ganttAddTask(g, "Progress Report 1")
g <- ganttAddTask(g, "Develop Draft of Activities 1-2", "2024-10-04", "2024-10-17", done=60)
g <- ganttAddTask(g, "Develop Draft of Activities 3-4", "2024-10-17", "2024-11-04", done=75)
g <- ganttAddTask(g, "Submit Tier 3 Proposal", "2024-10-17", "2024-10-24", done=0)
g <- ganttAddTask(g, "Progress Report 2")
g <- ganttAddTask(g, "Finalize Activity 1-2", "2024-11-03", "2024-11-17", done=0)
g <- ganttAddTask(g, "Finalize Activity 3-4", "2024-11-17", "2024-12-03", done=0)
g <- ganttAddTask(g, "Final Materials Submission")
g <- ganttAddTask(g, "Finalize applied R activity", "2024-12-01", "2024-12-10", done=0)
g <- ganttAddTask(g, "Finalize all activities and syllabus", "2024-12-10", "2024-12-14", done=0)


font <- ifelse(is.na(g[["start"]]), 2, 1)

plan::plot(g, ylabels=list(font=font),
     event.label='Progress Report 2', event.time='2024-11-01',
     col.event=c("firebrick2"),
     col.done=c("steelblue3"),
     col.notdone=c("palegreen3"),
     cex.main=1,
     main="Tier 2: Gentle Intro to Probability and Bayesian Statistics",
     )

legend("topright", pch=22, pt.cex=2, cex=0.6, pt.bg=c("steelblue3", "palegreen3"),
     border="black",
     legend=c("Completed", "Incomplete"), bg="white", xpd=TRUE)

```


## Meeting Times

We will keep meeting based on the following:

-   Weekly meetings for the activity-creating team
-   Monthly meetings with mentor (Mine)
-   Office hours

| Date       | Time               | PI     | Zoom Link |
|------------|--------------------|--------|-----------|
| 2024-11-07 |2:00 - 3:00 pm ET | Mine |[`r fontawesome::fa(name = "video")`](https://uci.zoom.us/j/96570454362) |
| 2024-11-12 | 3:00 - 4:00 pm ET      | Amy |   [`r fontawesome::fa(name = "video")`](https://duke.zoom.us/my/amyherring?pwd=UWczUjFOOXZ2MlhuYTMrLzVka05sQT09) password 11111       |
| 2023-11-20 | 3:45 - 4:45 pm ET | Monika |  [`r fontawesome::fa(name = "video")`](https://vassar.zoom.us/my/monika76five)        |

## Acknowledgements

This report template comes from Zachary Del Rosario and Stefani Langehennig's [Bayes-Bats tier 2 project](https://github.com/bayes-bats/tier2-freq-bayes)
